---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# icd: Interface to the International Classification of Diseases (ICD) API

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The [International Classification of Diseases (ICD)](https://www.who.int/standards/classifications/classification-of-diseases) serves a broad range of uses globally and provides critical knowledge on the extent, causes and consequences of human disease and death worldwide via data that is reported and coded with the ICD. [ICD API](https://icd.who.int/icdapi) allows programmatic access to the ICD. It is an HTTP based REST API. This package provides functions that interface with the ICD API.

## What does `icd` do?

## Installation

`icd` is not yet on CRAN.

You can install the development version of `icd` from [GitHub](https://github.com/OxfordIHTM/icd) with:

```{r gh-installation1, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("OxfordIHTM/icd")
```

then load `icd`

```{r gh-installation2, eval = FALSE}
# load package
library(icd)
```

## Usage

## Citation

If you find the `icd` package useful please cite using the suggested citation provided by a call to the `citation()` function as follows:

```{r citation}
citation("icd")
```

## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/OxfordIHTM/icd/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://oxford-ihtm.io/icd/CONTRIBUTING.html).

This project is released with a [Contributor Code of Conduct](https://OxfordIHTM/codeditr/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
