---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# icd: Interface to the International Classification of Diseases (ICD) API

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/OxfordIHTM/icd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OxfordIHTM/icd/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/OxfordIHTM/icd/branch/main/graph/badge.svg)](https://app.codecov.io/gh/OxfordIHTM/icd?branch=main)
<!-- badges: end -->

The [International Classification of Diseases (ICD)](https://www.who.int/standards/classifications/classification-of-diseases) serves a broad range of uses globally and provides critical knowledge on the extent, causes and consequences of human disease and death worldwide via data that is reported and coded with the ICD. [ICD API](https://icd.who.int/icdapi) allows programmatic access to the ICD. It is an HTTP based REST API. This package provides functions that interface with the ICD API.

## What does `icd` do?

Please note that `icd` is still highly experimental and is undergoing a lot of development. Hence, any functionalities described below have a high likelihood of changing interface or approach as we approach a stable working version.

### Authenticating with the ICD API

The ICD API uses OAuth2 for authentication. The package has a set of utility functions that support the ICD API authentication specifications leading to the generation of an OAuth2 token. The `icd_token()` function is the downstream and user-facing function that creates an ICD OAuth2 token that can be used by future functions that wrap ICD API for entity and linearization information retrieval.

An ICD OAuth2 token can be generated as follows:

```R
icd_token()
```

This function uses a built in OAuth2 application created for light use and for purposes of package development and testing.

It is recommended that those intending to use this package for programmatically performing high volume of calls to the ICD API to create their own **access keys** (`client id` and `client secret`) using [these instructions](https://icd.who.int/docs/icd-api/API-Authentication/).

Then, with your access keys, perform the following commands:


```R
## Create your own OAuth application ----
my_app <- icd_oauth_app(
  appname = "NAME_OF_YOUR_APP",
  key = "YOUR_CLIEND_ID",
  secret = "YOUR_CLIENT_SECRET"
)

## Create authentication token ----
my_token <- icd_token(app = my_app)
```

## Installation

`icd` is not yet on CRAN.

You can install the development version of `icd` from [GitHub](https://github.com/OxfordIHTM/icd) with:

```{r gh-installation1, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("OxfordIHTM/icd")
```

then load `icd`

```{r gh-installation2, eval = FALSE}
# load package
library(icd)
```

## Usage

## Citation

If you find the `icd` package useful please cite using the suggested citation provided by a call to the `citation()` function as follows:

```{r citation}
citation("icd")
```

## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/OxfordIHTM/icd/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://oxford-ihtm.io/icd/CONTRIBUTING.html).

This project is released with a [Contributor Code of Conduct](https://OxfordIHTM/codeditr/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
