---
title: "Get started with codigo"
author: Anita Makori and Ernest Guevarra
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get started with codigo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(codigo)
```

This article takes a quick tour of the main features of `codigo`. 

## Performing a basic search

A feature of the ICD API is the ability to search ICD 11 Foundation and ICD 11 Linearization for information regarding an illness/disease. This feature is captured by the `icd_search_foundation()` function. For example, if *colorectal cancer* is the disease of interest and information available from ICD 11 is needed, the following call can be made:

```{r search, eval = FALSE}
icd_search_foundation("colorectal cancer", client = my_oauth_client)
```

which gives the following output:

```{r result, echo = FALSE}
icd_search_foundation("colorectal cancer")
```

The output is a tibble created from parsed JSON body text of the HTTP response from the ICD API.

## Autocoding

Autocoding is a focused search that returns a single result based on the closest match from ICD-11. Autocoding using the ICD Foundation API endpoint produces



